The Bolocam Galactic Plane Survey: Survey Description and Data Reduction

### 2009-04-17 methods/ms.tex
distmaps

We present the Bolocam Galactic Plane Survey (BGPS), a 1.1 mm continuum survey
of \bgpsarea\ square degrees of the Galactic Plane primarily in the 1st
quadrant with some coverage in the 2nd and 3rd quadrants.  The BGPS represents
the first large area, systematic survey of the Northern Galactic Plane in the
millimeter continuum without pre-selected targets.  The survey has detected
\ncores\ clumps to a limiting depth of between \bgpsdepthlow\ and
\bgpsdepthhigh\ mJy RMS.  We include maps of 100 contiguous square degrees from
$\lon=-10.5$ to $\lon=86.5$ and $b=\pm0.5$ with a resolution of $\sim$35\arcsec, as
well as regions in IC1396, $\lon=111$ (NGC7538), W3/4/5, and Gem OB1.  The most
striking feature of the maps is the filamentary structure of cold dust
throughout the Galaxy.

>>>>

We present the Bolocam Galactic Plane Survey (BGPS), a 1.1 mm continuum survey
of \bgpsarea\ square degrees of the Galactic Plane with 130 in the 1st quadrant,
31 in the 2nd, and 6 in the 3rd.  The BGPS represents
the first large area, systematic survey of the Northern Galactic Plane in the
millimeter continuum without pre-selected targets.  The survey has detected
\ncores\ clumps to a limiting non-uniform 1-$\sig$ noise level in the range \bgpsdepthlow\ and
\bgpsdepthhigh\ mJy/beam RMS.  We present maps of 97 contiguous square degrees from
$\lon=-10.5$ to $\lon=86.5$ and $b=\pm0.5$ with a resolution of $\sim$35\arcsec, as
well as regions in IC1396, $\lon=111$ (NGC7538), W3/4/5, and Gem OB1.  The most
striking feature of the maps is the filamentary structure of millimeter emission
throughout the Galaxy.
